Computer Science House Constitution

### 2025-08-30 constitution.tex
change eligible votes to be semesterly

\asubsection{Semantic Changes}
\asubsubsection{Amendments}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
\asubsubsection{Compliance with RIT Policy and New York State Law}
Any change made to Article  \ref{ADHERENCE TO UNIVERSITY POLICIES} which is made due to an update in NY law or RIT policy may be treated as a Non-Semantic change.

\asubsubsection{Overrides}
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
The eligible voters for a vote are determined and fixed when the Voting Period begins.

@@

\asubsubsection{§ 120.16 Hazing in the first degree.}
A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
Hazing in the first degree is a class A misdemeanor.

\asubsubsection{§ 120.17 Hazing in the second degree.}
A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct, including, but not limited to, making physical contact with or requiring physical activity of such other person, which creates a substantial risk of physical injury to such other person or a third person.
Hazing in the second degree is a violation.

>>>>

\asubsection{Semantic Changes}
\asubsubsection{Amendments}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
\asubsubsection{Overrides}
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

@@

\asubsection{Eligible Votes}
The number of Active Members who are eligible to vote on the issue.
Following the first Intro Eval of the academic semester, Active Members are only eligible to vote if they have completed the qualifications listed in \ref{Expectations of Voting Members}.
Officers of CSH retain voting eligibility on all matters directly pertaining to the duties of their held office regardless of \ref{Expectations of Voting Members}.

@@

\asubsubsection{§ 120.16 Hazing in the first degree.}
A person is guilty of hazing in the first degree when, in the course of another person's initiation into or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person and thereby causes such injury.
Hazing in the first degree is a class A misdemeanor.

\asubsubsection{§ 120.17 Hazing in the second degree.}
A person is guilty of hazing in the second degree when, in the course of another person's initiation or affiliation with any organization, he intentionally or recklessly engages in conduct which creates a substantial risk of physical injury to such other person or a third person.
Hazing in the second degree is a violation.
